---
title: "Usage of eurusds and eur functions from exchangeratesr"
author: "Daniel Molnar"
date: 06-09-2019
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exchangeratesr-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Usage of "exchangeratesr" - vignette

This vignette contains examples showing the usage of the `eur` and `eurusds` functions form the `exchangeratesr` package.
In this example, my main goal is to visualize bitcoin prices and the amount sold each day using the `binancer` and `ggplot2` packages.

```{r, fig.show = 'hold'}
library(binancer)
library(data.table)
coin_prices <- binance_klines('BTCUSDT', interval = '1d', limit = 45)

balance <- coin_prices[, .(date = as.Date(close_time), btcusd = close, usd_volume = volume)]
head(balance)
```

Now that we have the balances and the BTC price, we load the exchangeratesr package and use the eurusds function to import historical values of EURUSD exchange rates.

```{r, fig.show = 'hold'}
library(exchangeratesr)
rates <- eurusds(Sys.Date() - 45, Sys.Date())

setkey(balance, date)
setkey(rates, date)

balance <- rates[balance, roll = TRUE]
balance[, eur_volume := usd_volume * btcusd * eurusd,]
head(balance)
```

Finally, visualize the values for the last 45 days and use the `eur` function to format EUR values.


```{r, fig.show = 'hold'}
library(ggplot2)

ggplot(data = balance, aes(x = date, y = eur_volume)) +
  geom_line(color = 'blue') +
  scale_y_continuous() +
  theme_bw() +
  labs(title = 'Total BTC value in the last 45 days',
       x = 'date',
       y = 'value in EUR')
```


